site_map

### 2020-09-16 site_map.Rmd
update

site_map 
```

>>>>

site_map

africa_map <- ggplot(africa_coast, aes(x = lon, y = lat)) + 
  theme_bw() + 
  coord_equal() + 
  geom_polygon(aes(group = group), colour = "black", fill = "grey80") + 
  geom_polygon(data = sa_provinces_new, (aes(group = group))) +
  annotate("text", label = "Africa", x = 16.0, y = 15.0, size = 3) + 
  theme(panel.border = element_rect(colour = "black", size = 0.4), 
        plot.background = element_blank(), 
        axis.ticks = element_blank(), 
        axis.text = element_blank(), 
        axis.title = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  coord_map(xlim = c(-20, 53), ylim = c(-36, 38), projection = "mercator") 
africa_map

sa_4 <- site_map +
annotation_custom(grob = ggplotGrob(africa_map),
xmin = 20.9, xmax = 26.9,
ymin = -30, ymax = -24)
sa_4
```
